---
title: "analysis"
author: "Joel Larwood"
date: "23/03/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

First I am going to install the tidyverse package
```{r}
library(tidyverse)
library(here)
library(readxl)
library(janitor)
```

Now I will import the data 
```{r}
data <- readxl::read_xlsx(here::here("data", "facebook_data.xlsx")) %>% 
  janitor::clean_names() %>% 
  dplyr::select(-id)

names(data)
```

Now I want to create scores for my variables

PANAS psotive is items  1, 3, 5, 9, 10, 12, 14, 16, 17

```{r}

data_vars_created <- data %>% 
  mutate(t1_panas_pos = rowSums(select(data, 
                                       panas01, 
                                       panas03, 
                                       panas05, 
                                       panas09, 
                                       panas10, 
                                       panas12, 
                                       panas14, 
                                       panas16, 
                                       panas17))) %>% 
  rowid_to_column(var = "id") # add id column to the data based of the row number

data_vars_created %>% # use the data frame called data 
  select(t1_panas_pos, #keeo thge t1_panas_pos variable
         id) %>% # keep the id variable
  glimpse()
```

```{r}

select_vars <- data_vars_created %>% 
  select(age, 
         gender, 
         education, 
         active_fbuse, 
         t1_panas_pos, 
         cort_t1)

glimpse(select_vars)

```

So now that we have the variables we want to analyse lets look at how much missing data there is and also the distributions 

```{r}
library(visdat)

visdat::vis_miss(select_vars)

```
Missing data is not a concern. Lkets look at the histograms 

```{r}

hist(select_vars$age)

hist(select_vars$gender)

hist(select_vars$active_fbuse)

hist(select_vars$t1_panas_pos)

hist(select_vars$cort_t1)

hist(select_vars$education)

```

So theres some issues in the data. We don't know which value is male and which is female. The cortisol is also skewed. 

Here we want to created new/fixed variables and we can use `mutate` to do that 

```{r}

data_to_analyse <- select_vars %>% 
  mutate(log_cortisol = log(select_vars$cort_t1), 
         gender_cat = if_else(select_vars$gender == 1, 
                              "male", 
                              "female"))


hist(data_to_analyse$log_cortisol) # get the histogram for the new cortisol values 

str(data_to_analyse$gender)
str(data_to_analyse$gender_cat)

```

```{r}
library(apaTables)

data_to_analyse %>%
  select(log_cortisol, 
         t1_panas_pos, 
         active_fbuse, 
         age) %>%  
 apa.cor.table(filename = here::here("output", "correlations.rtf")) 

```
Formula for regression in R is pretty trhe same as a hand written regression. 

DV ~ Predictor1 + Predictor2 + Predictor3 + Predictor2*Predictor3
```{r}
library(interactions)
library(sjPlot)

reg1 <- lm(log_cortisol ~ gender_cat, 
           data = data_to_analyse)

reg2 <- lm(log_cortisol ~ gender_cat + age, 
           data = data_to_analyse)

reg3 <- lm(log_cortisol ~ gender_cat + age + t1_panas_pos, 
           data = data_to_analyse)

reg4 <- lm(log_cortisol ~ gender_cat + age + t1_panas_pos + active_fbuse, 
           data = data_to_analyse)


sjPlot::tab_model(reg1, reg2, reg2, reg3, reg4, 
                  show.std = TRUE, 
                  show.aic = TRUE)

```

```{r}
mod_example <- lm(active_fbuse ~ gender_cat + t1_panas_pos + gender_cat*t1_panas_pos, 
                  data = data_to_analyse)

sjPlot::tab_model(mod_example,
                  show.std = TRUE, 
                  show.aic = TRUE)

sjPlot::plot_model(mod_example)

```


Hypothetically all the main effects were signinficant 
gender_male = .8 
t1_panas_pos = 1 
male*t1_panas_pos = 2 

male cortisol = .8 * 1 + 1 + 2 * 1

female cortisol = .8 + 0 + 1 + 2*0 




